\documentclass{report}

\usepackage[UKenglish]{babel}
\usepackage{datetime2}
\usepackage{listings}
\usepackage{xcolor}

%\definecolor{lstbg}{rgb}{0.5, 0.5, 0.5}

\lstdefinestyle{ogpdocstyle}{
  % commentstyle=\color{codegreen},
  % keywordstyle=\color{magenta},
  % numberstyle=\tiny\color{codegray},
  % stringstyle=\color{codepurple},
  % breakatwhitespace=false,         
  % breaklines=true,                 
  % captionpos=b,                    
  % keepspaces=true,                 
  % numbers=left,                    
  % numbersep=5pt,                  
  % showspaces=false,                
  % showstringspaces=false,
  % showtabs=false,                  
  % tabsize=2
  backgroundcolor = \color{lightgray},
  basicstyle = \ttfamily\footnotesize
}
\lstset{style = ogpdocstyle}

\newcommand{\OGP}{Open Geometry Prover}

\title{\OGP \linebreak Programmer Manual}
\author{Nuno Baeta \and Pedro Quaresma}
% \date{\DTMtoday}
% \date{Draft \DTMtoday}
\date{Draft \DTMtoday \ \DTMcurrenttime}

\begin{document}

\maketitle

\tableofcontents

\chapter{Introduction}
\label{chap:introduction}

This document:
\begin{itemize}
\item Defines a set of rules that every OGP prover must adhere;
\end{itemize}

As part of the OGP Community Project, contributions are welcome, whether
they are, e.g., provers or improvements to the definition of API.

\chapter{Common Settings}
\label{chap:commonsettings}

\begin{itemize}
\item Each prover must create a library and a stand-alone program
\item No programming language is enforced.  However, the languange must
  be available as free/libre and open source software (FLOSS).
\item Other tools must also be FLOSS.
\item The library must include a function to call the prover:
  \begin{itemize}
  \item it has only one argument, a file file with the conjecture;
  \item it must return codes and file with other information.  Other files may
    be created. The codes are: \ldots
  \end{itemize}
  If the library implements several provers, write one such function for
  each prover.
\item About stand-alone must adhere to a standard set of command line
  options.
  \begin{itemize}
  \item \ldots.
  \end{itemize}
\end{itemize}

\chapter{Provers}
\label{chap:provers}

\section{OGP GDDM}
\label{sec:ogpgddm}

\textbf{\texttt{dbRAM.hpp}}
\lstinputlisting[language=C++]{../../provers/ogpgddm/src/dbRAM.hpp}

\medskip
\textbf{\texttt{foftodb.hpp}}
\lstinputlisting[language=C++]{../../provers/ogpgddm/src/foftodb.hpp}

\medskip
\textbf{\texttt{prover.hpp}}
\lstinputlisting[language=C++]{../../provers/ogpgddm/src/prover.hpp}

\medskip
\textbf{\texttt{strs.hpp}}
\lstinputlisting[language=C++]{../../provers/ogpgddm/src/strs.hpp}

\medskip
\textbf{\texttt{version.hpp}}
\lstinputlisting[language=C++]{../../provers/ogpgddm/src/version.hpp}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
